Precise Spiking Motifs in Neurobiological and Neuromorphic~Data

### 2022-12-28 2022-12-28_coverletter.tex
brainsci-2069565_accepted

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for handling our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for your consideration as a review paper in \emph{Brain Sciences}. We are very grateful to the reviewers for their very insightful remarks and we have now responded to all their remarks.

In addition to our reports to reviewers, there is a tracked changes PDF file which highlights all changes.

>>>>

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for accepting our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for your consideration as a review paper in \emph{Brain Sciences}. We are very grateful to the reviewers for their very insightful remarks and we have now responded to all their remarks.

We have accepted all changes suggested at the proofreading stage and uploaded our files on the MDPI website.

### 2022-12-28 brainsci-2069565_accepted.tex
brainsci-2069565_accepted

%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{siunitx}%The siunitx package provides a  set  of  tools  for  authors  to  typeset  quantities  in  aconsistent  way.

\newcommand{\ms}{\si{\milli\second}}%

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Precise Spiking Motifs in Neurobiological and Neuromorphic~Data}
%
% MDPI internal command: Title for citation in the left column
\TitleCitation{Precise Spiking Motifs in Neurobiological and Neuromorphic Data}
%
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-3107-4788} % AnG % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-3916-0514} % AmG
\newcommand{\orcidauthorC}{0000-0002-0054-2729} % CB
\newcommand{\orcidauthorD}{0000-0002-9238-6654} % JN
\newcommand{\orcidauthorE}{0000-0001-8821-5556} % JM
\newcommand{\orcidauthorF}{0000-0002-9536-010X} % LP
%
% Authors, for the paper (add full first names)
\Author{\hl{Antoine Grimaldi} %MDPI: Please carefully check the accuracy of names and affiliations.
 $^{1}$% $^{1,\dagger,\ddagger}$
\orcidA{}, 
Amélie Gruel $^{2}$\orcidB{}, % $^{2,\dagger,\ddagger}$,
Camille Besnainou $^{1}$\orcidC{},
\hl{Jean-Nicolas Jérémie} %MDPI: The name of this author is different from the one submitted online at susy.mdpi.com. Please confirm which one is correct.
 $^{1}$\orcidD{},
Jean Martinet $^{2}$\orcidE{}
and~\hl{Laurent Perrinet} %MDPI: The name of this author is different from the one submitted online at susy.mdpi.com. Please confirm which one is correct.
 $^{1,}$*\orcidF{}}
%
%\longauthorlist{yes}
%
% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Antoine Grimaldi, Amélie Gruel, Camille Besnainou, Jean-Nicolas Jérémie, Jean Martinet and Laurent Perrinet}
%
% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Grimaldi, A.; Gruel, A.; Besnainou, C.; Jérémie, J.-N.; Martinet, J.; Perrinet, L.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
%
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad \hl{INT UMR 7289, Aix Marseille Univ, CNRS, 27 Bd Jean Moulin,} %Please confirm whether the address information is correct.
13005 Marseille, France; \hl{antoine.grimaldi@univ-amu.fr (A.G.); camille.besnainou@etu.univ-amu.fr (C.B.)} %MDPI: We added the email addresses here according to those submitted online at susy.mdpi.com. Please confirm.
 \\
$^{2}$ \quad \hl{SPARKS,  Côte d'Azur, CNRS, I3S, 2000 Rte des Lucioles,} %Please confirm whether the address information is correct.
06900 Sophia-Antipolis, France; \hl{amelie.gruel@i3s.unice.fr (A.G.); jean.martinet@univ-cotedazur.fr (J.M.)} %MDPI: We added the email addresses here according to those submitted online at susy.mdpi.com. Please confirm.

}
%
% Contact information of the corresponding author
\corres{Correspondence: laurent.perrinet@univ-amu.fr}
%
% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3.} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes
%
%\simplesumm{} % Simple summary
%
%\conference{} % An extended version of a conference paper
%
% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Why do neurons communicate through spikes? By definition, spikes are all-or-none neural events which occur at continuous times. In other words, spikes are on one side binary, existing or not without further details, and on the other, can occur at any asynchronous time, without the need for a centralized clock. This stands in stark contrast to the analog representation of values and the discretized timing classically used in digital processing and at the base of modern-day neural networks. As neural systems almost systematically use this so-called event-based representation in the living world, a better understanding of this phenomenon remains a fundamental challenge in neurobiology in order to better interpret the profusion of recorded data. With the growing need for intelligent embedded systems, it also emerges as a new computing paradigm to enable the efficient operation of a new class of sensors and event-based computers, called neuromorphic, which could enable significant gains in computation time and energy consumption---a major societal issue in the era of the digital economy and global warming. In this review paper, we provide evidence from biology, theory and engineering that the precise timing of spikes plays a crucial role in our understanding of the efficiency of neural networks.
}
%
% Keywords
\keyword{\textls[-15]{spikes; asynchronous computing; neurobiology; computational neuroscience; neuromorphic} engineering; heterogeneous delays; spiking motifs; polychronization} 
%
% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

>>>>

%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{siunitx}%The siunitx package provides a  set  of  tools  for  authors  to  typeset  quantities  in  aconsistent  way.
\newcommand{\ms}{\si{\milli\second}}%

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Precise Spiking Motifs in Neurobiological and Neuromorphic~Data}
% MDPI internal command: Title for citation in the left column
\TitleCitation{Precise Spiking Motifs in Neurobiological and Neuromorphic Data}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-3107-4788} % AnG % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-3916-0514} % AmG
\newcommand{\orcidauthorC}{0000-0002-0054-2729} % CB
\newcommand{\orcidauthorD}{0000-0002-9238-6654} % JN
\newcommand{\orcidauthorE}{0000-0001-8821-5556} % JM
\newcommand{\orcidauthorF}{0000-0002-9536-010X} % LP
% Authors, for the paper (add full first names)
\Author{Antoine Grimaldi $^{1}$% $^{1,\dagger,\ddagger}$
\orcidA{}, 
Amélie Gruel $^{2}$\orcidB{}, % $^{2,\dagger,\ddagger}$,
Camille Besnainou $^{1}$\orcidC{},
Jean-Nicolas Jérémie $^{1}$\orcidD{},
Jean Martinet $^{2}$\orcidE{}
and~Laurent U Perrinet $^{1,}$*\orcidF{}}
%\longauthorlist{yes}
% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Antoine Grimaldi, Amélie Gruel, Camille Besnainou, Jean-Nicolas Jérémie, Jean Martinet and Laurent U Perrinet}
% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Grimaldi, A.; Gruel, A.; Besnainou, C.; Jérémie, J.-N.; Martinet, J.; Perrinet, L.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad INT UMR 7289, Aix Marseille Univ, CNRS, 27 Bd Jean Moulin, 13005 Marseille, France; antoine.grimaldi@univ-amu.fr (A.G.); camille.besnainou@etu.univ-amu.fr (C.B.); jean-nicolas.jeremie@univ-amu.fr (J.-N.J.), laurent.perrinet@univ-amu.fr (L.U.P.)
 \\
$^{2}$ \quad SPARKS,  Côte d'Azur, CNRS, I3S, 2000 Rte des Lucioles,
06900 Sophia-Antipolis, France; amelie.gruel@i3s.unice.fr (A.G.); jean.martinet@univ-cotedazur.fr (J.M.)
% Contact information of the corresponding author
\corres{Correspondence: laurent.perrinet@univ-amu.fr}
% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3.} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes
%\simplesumm{} % Simple summary
%\conference{} % An extended version of a conference paper
% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Why do neurons communicate through spikes? By definition, spikes are all-or-none neural events which occur at continuous times. In other words, spikes are on one side binary, existing or not without further details, and on the other, can occur at any asynchronous time, without the need for a centralized clock. This stands in stark contrast to the analog representation of values and the discretized timing classically used in digital processing and at the base of modern-day neural networks. As neural systems almost systematically use this so-called event-based representation in the living world, a better understanding of this phenomenon remains a fundamental challenge in neurobiology in order to better interpret the profusion of recorded data. With the growing need for intelligent embedded systems, it also emerges as a new computing paradigm to enable the efficient operation of a new class of sensors and event-based computers, called neuromorphic, which could enable significant gains in computation time and energy consumption---a major societal issue in the era of the digital economy and global warming. In this review paper, we provide evidence from biology, theory and engineering that the precise timing of spikes plays a crucial role in our understanding of the efficiency of neural networks.
% Keywords
\keyword{\textls[-15]{spikes; asynchronous computing; neurobiology; computational neuroscience; neuromorphic} engineering; heterogeneous delays; spiking motifs; polychronization} 
% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}
% Only for the journal Diversity
%\LSID{\url{http://}}
